\documentclass{article}
\usepackage{listings}

\begin{document}

\section*{Questions}

\subsection*{MATH 235 (Algebra 1)}

\begin{enumerate}
\item Let $A = \{1, 2, 3, 4, 5\}$ and $B = \{4, 5, 6, 7, 8\}$. Compute $A \cup B$ and $A \cap B$.
\item Prove that $(A \cup B) - B = A - B$ for any sets $A$ and $B$.
\item Let $f: \mathbb{R} \to \mathbb{R}$ be defined by $f(x) = x^2$. Is $f$ injective? Is $f$ surjective?
\item Prove that the sum of a rational number and an irrational number is irrational.
\item Prove that there are infinitely many prime numbers.
\item Let $z = a + bi$ be a complex number, where $a, b \in \mathbb{R}$. Prove that $|z|^2 = z \cdot \overline{z}$.
\item Let $z, w \in \mathbb{C}$. Prove that $|zw| = |z||w|$.
\item Let $A = \begin{bmatrix} a & b \\ c & d \end{bmatrix}$ be a $2 \times 2$ matrix. Prove that the characteristic polynomial of $A$ is $\lambda^2 - \text{tr}(A)\lambda + \det(A)$.
\end{enumerate}

\subsection*{MATH 222 (Calculus 3)}

\begin{enumerate}
\item Compute the Taylor series expansion of $\sin(x)$ at $x = 0$ up to the $x^4$ term.
\item Let $f(x, y) = x^2y - y^3$. Compute $\partial f/\partial x$ and $\partial f/\partial y$.
\item Compute the double integral $\iint_R (2x - y) \, dA$, where $R$ is the rectangle with vertices $(1, 0)$, $(2, 0)$, $(1, 1)$, $(2, 1)$.
\item Let $\mathbf{F}(t) = (t^2, t^2)$ and $C$ be the line segment from $(0, 0)$ to $(1, 1)$. Compute the line integral $\int_C \mathbf{F} \cdot d\mathbf{r}$.
\item Let $f(x, y, z) = x^2 + y^2 + z^2$. Compute the gradient $\nabla f$.
\item Let $\mathbf{F}(x, y, z) = (x, y, z)$. Compute the curl of $\mathbf{F}$.
\item Let $\mathbf{F}(x, y, z) = (x, y, z)$. Compute the divergence of $\mathbf{F}$.
\item Let $\mathbf{F}(x, y, z) = (x, y, z)$ and $S$ be the unit sphere. Compute the surface integral $\iint_S \mathbf{F} \cdot d\mathbf{S}$.
\end{enumerate}

\subsection*{MATH 242 (Analysis 1)}

\begin{enumerate}
\item Prove that the sequence $\{1/n\}$ converges to 0.
\item Let $\{a_n\}$ be a sequence defined by $a_1 = 1$ and $a_{n+1} = (1/2)(a_n + 2/a_n)$ for all $n \geq 1$. Prove that the sequence $\{a_n\}$ converges.
\item Prove that the series $\sum_{n=1}^\infty 1/n^2$ converges.
\item Let $f(x) = x^2$. Prove that $f$ is continuous at $x = 1$.
\item Let $f(x) = 1/x$. Prove that $f$ is not uniformly continuous on $(0, 1)$.
\item Let $f(x) = x^2$. Prove that $f$ is differentiable at $x = 1$.
\item Let $f(x) = |x|$. Prove that $f$ is not differentiable at $x = 0$.
\item Let $f(x) = x^3$. Prove that $f$ is uniformly continuous on $\mathbb{R}$.
\end{enumerate}

\subsection*{COMP 273 (Introduction to Computer Systems)}

\begin{enumerate}
\item Convert the binary number 101101 to decimal.
\item Convert the hexadecimal number A3 to binary.
\item Design a simple combinational circuit with two inputs, A and B, and one output, F, such that F = 1 if and only if exactly one of A and B is 1.
\item Write a MIPS assembly program that computes the factorial of a non-negative integer n.
\item What is a direct-mapped cache?
\item What is virtual memory?
\item How does pipelining improve the performance of a computer?
\item What is an interrupt?
\end{enumerate}

\subsection*{COMP 206 (Introduction to Software Systems)}

\begin{enumerate}
\item Write a C program that prints "Hello, world!" to the console.
\item What is a system call?
\item What is a library in C?
\item What is a makefile?
\item What are version control systems?
\item What is debugging?
\item What is testing?
\item What is a pointer in C?
\end{enumerate}

\end{document}
